%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
 \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Anurag kushwaha} \\ \vspace{1pt}
    \small +91 8587822762 $|$ \href{mailto:anuragkush051@gmail.com}{\underline{anuragkush051@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/anurag0s1/}{\underline{linkedin.com/in/anurag0s1/}} $|$
    \href{https://github.com/ANURAG0S1}{\underline{github.com/ANURAG0S1}}
\end{center}


%-----------PROGRAMMING SKILLS-----------
\section{PROFESSIONAL SUMMARY}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      Frontend Engineer with 2+ years of relevant experience working in small and large teams to develop
interactive, user-friendly, and feature-rich web applications. A self-motivated and lifelong learner with expertise
in developing scalable UI applications in JavaScript/TypeScript with 10+ million users by adhering to UI
architectural best practices.

    }}
 \end{itemize}


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript/ES6, HTML/CSS, TypeScript,SASS, SQL} \\
     \textbf{Frameworks}{: React, Angular, Node.js,Express.JS,BootStrap, Tailwind } \\
     \textbf{Libraries}{: Material UI, Axios, RxJS}\\
     \textbf{Tools}{: Git, Docker, NPM, Jenkins, Google Cloud Platform, VS Code, Grafana} \\
   
    }}
 \end{itemize}
%



%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Frontend Executive}{  August 2023 -- Present }
      {Adani Digital Labs}{Gurgaon, IN}
      \resumeItemListStart
        \resumeItem{ Maintained integration plugin of trainman providing trains feature on
Adani one App.}
        \resumeItem{Intergrated third party APIs like IRCTC, razorpay, AdPushup, Google Ad \& analytics.}
        \resumeItem{Conducted comprehensive code reviews to ensure the maintenance of
high code quality standards, offering valuable suggestions and
enhancements to fellow developers.}
  \resumeItem{Worked with various libraries like RxJS, momentJS, MaterialUI.}
  \resumeItem{Implemented security best practices, including input validation, secure
authentication mechanisms, and protection against common
vulnerabilities like XSS and CSRF.}
      \resumeItemListEnd

 
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Software Engineer}{December 2021 -- July 2023  }
      {Trainman}{Gurgaon, IN}
      \resumeItemListStart
        \resumeItem{White Label Solution : Created integration plugin of trainman, utilising
same onBoarded 3 companies}
        \resumeItem{Well-versed in building responsive and dynamic web applications with an
emphasis on usability, performance, and accessibility.}
 \resumeItem{Iterated user interfaces (homepage, search, profile, bookings, payments, etc) to simplify search functionality and payment processes.}



        \resumeItem{Implemented Services to manage google ads and analytics. }
  \resumeItem{Successfully migrated the Angular codebase from v9 to v13, resulting in
a 30\% improvement in application performance.}
  \resumeItem{Implemented SSR for better SEO ranking and reduced page load time
from 6s to 2.5s.} 
\resumeItem{ Performance monitoring with tools like Lighthouse and New Relic to
identify bottlenecks and improve web application performance.}
    \resumeItemListEnd


 

    \resumeSubheading
      {Frontend Engineer}{Septmeber 2020 -- December 2020 }
      {RYD Labs --- remote}{Noida, IN}
      \resumeItemListStart
        \resumeItem{Involved in planning feature implementation strategies and end to end
implementation of product features.}
        
\resumeItem{  Successfully resolved complex UI/UX challenges by leveraging React's
component lifecycle, custom hooks, and third-party libraries}
\resumeItem{ Transformed Figma design into a high-performance web app
using React, and CSS, resulting in 20\% higher
engagement.}


    \resumeItemListEnd

 
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      
      \resumeProjectHeading
          {\textbf{Today's Recipe} $|$ \emph{Spoonacular API, React.JS, JavaScript, Node.JS, Git}} {}
          \resumeItemListStart
             \resumeItem{ Developed a dynamic recipe application using Spoonacular API, integrating real-time data retrieval and display using React.JS and Node.JS.}
            \resumeItem{One can submit the mood/taste of ideal food they want to eat, based on the preferences, food recipes are populated.}
            \resumeItem{Integrated user authentication and authorization features using JWT and bcrypt, ensuring secure access and data protection.}
            \resumeItem{Employed Node.JS for backend development, leveraging Express to build robust APIs that supported application functionalities such as user preferences and recipe bookmarking.}
         
           
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Starex University}{Gurgaon, Haryana}
      {Bachelor of Technology in Computer Science}{April 2019 -- May 2023}
   
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
